% ---------------------------------------------------------------
\chapter{The Modules}
\label{section:the_modules}
% ---------------------------------------------------------------

Some text here

% ---------------------------------------------------------------
\section{The Module directory}
% ---------------------------------------------------------------

This contains all the python worker files for the DRS. The file structure is as below.

\customdirtree{%
.1 \{DIR\}.
.2 \{INSTALL\_ROOT\}.
.3 DRS\_SPIROU.
.4 python.
.5 Modules.
.6 hadgtVISU.
.7 \DTcomment{hadmrVISU module files}.
.6 hadmrBACK.
.7 \DTcomment{hadmrBACK module files}.
.6 hadmrBIAS.
.7 \DTcomment{hadmrBIAS module files}.
.6 hadmrCDB.
.7 \DTcomment{hadmrCDB module files}.
.6 hadmrDARK.
.7 \DTcomment{hadmrDARK module files}.
.6 hadmrEXTOR.
.7 \DTcomment{hadmrEXTOR module files}.
.6 hadmrFITS.
.7 \DTcomment{hadmrFITS module files}.
.6 hadmrFLAT.
.7 \DTcomment{hadmrFLAT module files}.
.6 hadmrLED.
.7 \DTcomment{hadmrLED module files}.
.6 hadmrLOCOR.
.7 \DTcomment{hadmrLOCOR module files}.
.6 hadmrMATH.
.7 \DTcomment{hadmrMATH module files}.
.6 hadmrRV.
.7 \DTcomment{hadmrRV module files}.
.6 hadmrSIMU.
.7 \DTcomment{hadmrSIMU module files}.
.6 hadmrTHORCA.
.7 \DTcomment{hadmrTHORCA module files}.
.6 hadrgdCONFIG.
.7 \DTcomment{hadrgdCONFIG module files}.
.6 spirouBACK.py.
.6 spirouBIAS.py.
.6 spirouCDB.py.
.6 spirouEXTOR.py.
.6 spirouFITS.py.
.6 spirouFLAT.py.
.6 spirouLOCOR.py.
.6 spirouRV.py.
.6 spirouTHORCA.py.
.6 spirouVISU.py.
}

\section{spirouBACK}
spirouBACK.py contains functions to calculate the detector background
\section{spirouCDB}
spirouCDB.py: contains functions for the calibrations database (infos for master\_calib.txt, and to coy files in the caliDB directory)
\section{spirouEXTOR}
spirouEXTOR.py: contains function for the ordres extraction
\section{spirouFITS}
spirouFITS.py: contains functions to read FITS file and copy keywords
\section{spirouLOCOR}
spirouLOCOR.py: contains functions for order localization
\section{spirouRV}
spirouRV.py: contains functions to compute radial velocity
\section{spirouVISU}
spirouVISU.py: contains functions for visualization